Community-Conditioned Language Models

### 2021-05-04 paper/paper.tex
fixes and tweaks

Computing this distance is known as the Procrustes problem. Its
solution is

\[d(L,S) = \mathsf {Tr} Σ\], where the \(Σ\) is obtained by the singular value
decomposition \(U^TΣV = LS^T\).  The vectors of \(U\) and \(V\) give
the directions of correlation respectively of \(L\) and \(S\). The
singular values \(\sigma_i\) (diagonal elements of \(Σ\)), say how much
correlation there is between the directions \(U_i\) and \(V_i\).

Further we can arrange the solution so that \(σ_i < σ_j\) iff \(i < j\). That
is, the largest singular value \(σ_0\) corresponds to the principal
direction of correlation (\(U_0\), \(V_0\)), \(σ_1\) to the second
principal direction, etc.

The \(d(L,S)\) metric varies between \(0\) (perfect independence) and
\(n\) (perfect correlation, obtained for example if \(L=S\)).

To get a sense of what value of \(d(L,S)\) indicates significant correlation,
We have computed experimentally \(d(L,S)\) for 
\(L\) and \(S\) chosen at random and 16 dimensions. We find
a mean of TODO and a standard deviation of TODO.

Thus \(d(L,S)\) above \(μ+3σ\) can be safely considered to indicate a
statistically significant correlation between \(L\) and
\(S\). However, below, we will also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\).

>>>>

Computing this distance is known as the orthogonal Procrustes problem~\citep{Gower2004}. Its
solution is
\[d(L,S) = \mathsf {Tr} Σ\] where the matrix \(Σ\) is obtained by the singular value
decomposition \(U^TΣV = LS^T\). Additionally the vectors of \(U\) and \(V\) give
the directions of correlation respectively of \(L\) and \(S\). The
singular values \(\sigma_i\) (diagonal elements of \(Σ\)), say how much
correlation there is between the directions \(U_i\) and \(V_i\).

Further, we can arrange the solution so that \(σ_i < σ_j\) iff \(i < j\). That
is, the largest singular value \(σ_0\) corresponds to the principal
directions of correlation (\(U_0\), \(V_0\)), \(σ_1\) to the second
principal direction, etc.

The \(d(L,S)\) metric varies between \(0\) (perfect independence) and
\(n\) (perfect correlation, obtained for example if \(L=S\)), where
$n$ is the number of community embeddings considered.

To get a more precise sense of what value of \(d(L,S)\) indicates significant correlation,
We have computed experimentally \(d(L,S)\) for 
\(L\) and \(S\) chosen at random and 16 dimensions. We find
a mean of TODO and a standard deviation of TODO.

Thus \(d(L,S)\) below \(μ-3σ\) can be safely considered to indicate a
statistically significant correlation between \(L\) and
\(S\). However, below, we will also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\).
